%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Xiyu Zhai} % Your name
\address{235 Albany Street, Cambridge, MA 02139} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+1)8574724363 \\ xiyuzhai@mit.edu} % Your phone number and email
\usepackage{bibentry}
\begin{document}
\nobibliography{ref}
  \bibliographystyle{unsrt}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Massachusetts Institute of Techology} \hfill {\em August 2018 - Present} 
\\ PhD Candidate, EECS Department
\\ Major: Programming Language for AI
\\{\bf University of Cambridge}\hfill {\em October 2017 - June 2018} 
\\ Master of Advanced Studies in Part III Mathematics
\\ Major: Pure Mathematics and Statistics
\\ Grades: Distinction
\\{\bf University of Science and Technology of China} \hfill {\em August 2013 - July 2017} 
\\ Bachelor of Science
\\ Major: Pure Mathematics
\\ Department of Mathematical Sciences\\\hfill { GPA: 4.11/4.3, Rank: \#1 }

\end{rSection}

\begin{rSection}{Research}
\begin{itemize}
	\item 

Programming Language for AI.

I'm implementing an programming system (language+analyzer+debugger+visualizer) that enables advanced learning-augmented programming across multiple domains, including pattern recognition in computer vision, learning-based rendering, video compression, RL, theorem proving, etc.

The immediate goal now is to make a very fast, fully interpretable, provably robust classifier for images (which must be different from deep learning in every possible way).

Have started pursuing this goal even before PhD. It started as a theoretical project, but recently it has transformed into a programming language project.

Expect to finish the first round of results before the start of my fifth year of PhD.
\item Number Theory.

I'm simultaneously interested in Number Theory itself and rewriting existing proofs into machine checkable ones, just like Xena project.

Still learning the basics.
\end{itemize}

\end{rSection}

\begin{rSection}{Programming Technique}
\begin{itemize}
	\item C++. Have experience writing and managing a codebase of 30k+ lines of code. But I know the language well enough to prefer Rust.
	\item Rust. My major language. I'm use Rust mostly in my PhD project, 16k lines of code.
	\item Javascript/Typescript. I use it for gui development. I had experience with React but now I'm using Svelte.
	\item Python. Have experience with it during internship and past immature attempts of my PhD project.
	\item Haskell. Didn't programmed much in it, but immitate many of its features in my project.
\end{itemize}
\end{rSection}

\begin{rSection}{Publication}

I've not yet finish anything publishable in my PhD project. So the following doesn't reflect much about what I'm doing right now.

\begin{enumerate}
	\item \bibentry{colt18}
	\item \bibentry{colt19}
	\item \bibentry{iclr18}
	\item \bibentry{nips18}
	\item \bibentry{icml19}
	\item \bibentry{arXiv19}
\end{enumerate}
\end{rSection}
\end{document}